Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Updated all prepan plots with GLAD/EDGI prepan subset data

GLAD.prepan %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")

@@

GLAD.prepan %>% 
  ggplot(aes(x = age_category_collapsed)) +
  geom_bar(fill = COPINGpalette9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "")

@@

GLAD.prepan_ethnicity_plot <- dat.retro %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
             "White" = "European",
             "Asian or Asian British" = "Asian or Asian British",
             "Black or Black British" = "African or African British",
             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
             "Other" = "Other"
           ))

GLAD.prepan_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

@@

GLAD.prepan %>% 
  ggplot(aes(x = employment_prior_covid)) +
  geom_bar(fill = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "")

@@

GLAD.prepan <- GLAD.prepan %>% 
  mutate(personality_disorder_numeric =
           case_when(
             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
           ))

@@

GLAD.prepan_mdd_positive <- GLAD.prepan %>%
  select(depressive_disorders_numeric) %>% 
  filter(depressive_disorders_numeric == 1)

@@

GLAD.prepan_anxi_positive <- GLAD.prepan %>%
  select(anxiety_disorders_numeric) %>% 
  filter(anxiety_disorders_numeric == 1)

@@

GLAD.prepan_ED_positive <- GLAD.prepan %>%
  select(eating_disorders_numeric) %>% 
  filter(eating_disorders_numeric == 1)

@@

GLAD.prepan_OCD_positive <- GLAD.prepan %>%
  select(obsessive_compulsive_disorders_numeric) %>% 
  filter(obsessive_compulsive_disorders_numeric == 1)

@@

GLAD.prepan_psychosis_positive <- GLAD.prepan %>%
  select(psychotic_disorders_numeric) %>% 
  filter(psychotic_disorders_numeric == 1)

@@

GLAD.prepan_ASD_positive <- GLAD.prepan %>%
  select(autism_spectrum_disorder_numeric) %>% 
  filter(autism_spectrum_disorder_numeric == 1)

@@

GLAD.prepan_ADHD_positive <- GLAD.prepan %>%
  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)

@@

GLAD.prepan_PD_positive <- GLAD.prepan %>%
  select(personality_disorder_numeric) %>% 
  filter(personality_disorder_numeric == 1)

@@

GLAD.prepan_BD_positive <- GLAD.prepan %>%
  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)

@@

GLAD.prepan_PTSD_positive <- GLAD.prepan %>%
  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)

@@

GLAD.prepan_control_positive <- GLAD.prepan %>%
  select(control_numeric) %>% 
  filter(control_numeric == 1)

>>>>

GLAD.prepan_with_EDGI %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "N participants")

@@

GLAD.prepan_with_EDGI %>% 
  ggplot(aes(x = age_category_collapsed)) +
  geom_bar(fill = COPINGpalette9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "")

@@

GLAD.prepan_ethnicity_plot <- GLAD.prepan_with_EDGI %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
             "White" = "European",
             "Asian or Asian British" = "Asian or Asian British",
             "Black or Black British" = "African or African British",
             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
             "Other" = "Other"
           ))

GLAD.prepan_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

@@

GLAD.prepan_with_EDGI %>% 
  ggplot(aes(x = employment_prior_covid)) +
  geom_bar(fill = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "")

@@

GLAD.prepan_with_EDGI <- GLAD.prepan_with_EDGI %>% 
  mutate(personality_disorder_numeric =
           case_when(
             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
           ))

@@

GLAD.prepan_mdd_positive <- GLAD.prepan_with_EDGI %>%
  select(depressive_disorders_numeric) %>% 
  filter(depressive_disorders_numeric == 1)

@@

GLAD.prepan_anxi_positive <- GLAD.prepan_with_EDGI %>%
  select(anxiety_disorders_numeric) %>% 
  filter(anxiety_disorders_numeric == 1)

@@

GLAD.prepan_ED_positive <- GLAD.prepan_with_EDGI %>%
  select(eating_disorders_numeric) %>% 
  filter(eating_disorders_numeric == 1)

@@

GLAD.prepan_OCD_positive <- GLAD.prepan_with_EDGI %>%
  select(obsessive_compulsive_disorders_numeric) %>% 
  filter(obsessive_compulsive_disorders_numeric == 1)

@@

GLAD.prepan_psychosis_positive <- GLAD.prepan_with_EDGI %>%
  select(psychotic_disorders_numeric) %>% 
  filter(psychotic_disorders_numeric == 1)

@@

GLAD.prepan_ASD_positive <- GLAD.prepan_with_EDGI %>%
  select(autism_spectrum_disorder_numeric) %>% 
  filter(autism_spectrum_disorder_numeric == 1)

@@

GLAD.prepan_ADHD_positive <- GLAD.prepan_with_EDGI %>%
  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)

@@

GLAD.prepan_PD_positive <- GLAD.prepan_with_EDGI %>%
  select(personality_disorder_numeric) %>% 
  filter(personality_disorder_numeric == 1)

@@

GLAD.prepan_BD_positive <- GLAD.prepan_with_EDGI %>%
  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)

@@

GLAD.prepan_PTSD_positive <- GLAD.prepan_with_EDGI %>%
  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)

@@

GLAD.prepan_control_positive <- GLAD.prepan_with_EDGI %>%
  select(control_numeric) %>% 
  filter(control_numeric == 1)
